---
title: "Rebecca N Checkpoint E"
output: html_notebook
author: "Rebecca Neal"
date: " 23 April 2020"
version: "version 1.0"
---

This is Checkpoint E for EDRM 718

### Q1 What is the name of the package that must be installed for all things in the tidyverse
#### Answer: tidyverse - going to load it while we are here
```{r include=FALSE}
library(tidyverse)
library(ggplot2)
```

### Q2 Import Small Cities Health Data into a tibble named "health"
```{r}
health <- read_csv("Small Cities Health Data.csv")
health
```

### Q3 - Convert the helath tibble to a data frame and back to a tibble
```{r}
health <- as_data_frame(health)
health <- as_tibble(health)
```

### Q4 Create scatterplot to show relationship of # of physicians to # hospital beds
```{r}
health %>%
  ggplot(aes(x = hosp.beds, y = doctors)) +
  geom_point()

```

### Q5 - Construct same plot but only use cities with less than 1000 hospital beds
```{r}
health_plot <- health %>%
  filter(hosp.beds < 1000) %>%
  ggplot(aes(x = hosp.beds, y = doctors)) +
  geom_point()
health_plot
```

### Q6 - Add a regression line for Q5
```{r}
health_plot <- health %>%
  filter(hosp.beds < 1000) %>%
  ggplot(aes(x = hosp.beds, y = doctors)) +
  geom_point()+
  stat_smooth(method = "lm")
health_plot
```

### Q7 - Add population density from the Small Cities Densities to the health tibble
#### First, we need to load in the Small Cities data make sure there are no duplicates
```{r}
cities <- read_csv("Small Cities Densities.csv")

check_cities <- cities %>%
  filter (n > 1)

cities

```

#### Now we can add the variable
```{r}
health2 <- health %>%
  left_join(cities, by = "city.code")

```

### Q8 - Add a categorical variable for Low Medium and High density
```{r}
health3 <- health2%>%
  mutate(cat.density = cut(density,
                           breaks = c(0, 80, 120, 300),
                           labels = c("Low", "Medium", "High")))
```

### Q9 Construct a scatterplot but add regression lines for each category of density
```{r}
health_plot2 <- health3 %>%
  filter(hosp.beds < 1000) %>%
  ggplot(aes(x = hosp.beds, y = doctors, color = cat.density)) +
  geom_point() +
  stat_smooth(method = "lm", se = FALSE)
health_plot2
```

### Q10 Do the same thing we did in Q9 but add labels
```{r}
health_plot2 <- health3 %>%
  filter(hosp.beds < 1000) %>%
  ggplot(aes(x = hosp.beds, y = doctors, color = cat.density)) +
  geom_point() +
  stat_smooth(method = "lm", se = FALSE) +
  labs(x = "Number of Hospital Beds",
       y = "Number of Doctors",
       title = "Relationship of Doctors to Hospital Beds", 
       subtitle = "Regression Lines for Low, Medium, and High Density Cities")
health_plot2
```

### Q11 - Read the Patient Data and remove the word patients
```{r}
patients <- read_csv("Patient Data.csv")
```

patients$patient <- as_factor(patients$patient)

#### trying fresh
```{r}

patients2 <- patients %>%
  transmute(ID = str_replace_all(patient, "Patient", ""))
```


### Q12 - Tidy the Patient Data
```{r}
patients %>%
  gather(reading.1, reading.2, reading.3, key = "Round", value = "Reading")
```




